\documentclass[12pt,a4paper,titlepage]{article}
\usepackage[a4paper]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{lipsum}
\usepackage{cite}
\usepackage[normalem]{ulem}

\usepackage{amsmath, amssymb, amsfonts, amsthm, fouriernc, mathtools}
% mathtools for: Aboxed (put box on last equation in align envirenment)
\usepackage{microtype} %improves the spacing between words and letters

\usepackage{graphicx}
\graphicspath{ {./pics/} {./eps/}}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{fancyhdr}
\usepackage{float}
\setlength{\headheight}{15.2pt}
\pagestyle{fancy}
\lhead{afranzoni3 \& hghabelzadeh3}
\rhead{Page \thepage}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% COLOR DEFINITIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[svgnames]{xcolor} % Enabling mixing colors and color's call by 'svgnames'
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\definecolor{MyColor1}{rgb}{0.2,0.4,0.6} %mix personal color
\newcommand{\textb}{\color{Black} \usefont{OT1}{lmss}{m}{n}}
\newcommand{\blue}{\color{MyColor1} \usefont{OT1}{lmss}{m}{n}}
\newcommand{\blueb}{\color{MyColor1} \usefont{OT1}{lmss}{b}{n}}
\newcommand{\red}{\color{LightCoral} \usefont{OT1}{lmss}{m}{n}}
\newcommand{\green}{\color{Turquoise} \usefont{OT1}{lmss}{m}{n}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% FONTS AND COLORS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    SECTIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{titlesec}
\usepackage{sectsty}
%%%%%%%%%%%%%%%%%%%%%%%%
%set section/subsections HEADINGS font and color
\sectionfont{\color{MyColor1}}  % sets colour of sections
\subsectionfont{\color{MyColor1}}  % sets colour of sections

%set section enumerator to arabic number (see footnotes markings alternatives)
\renewcommand\thesection{\arabic{section}.} %define sections numbering
\renewcommand\thesubsection{\thesection\arabic{subsection}} %subsec.num.

%define new section style
\newcommand{\mysection}{
\titleformat{\section} [runin] {\usefont{OT1}{lmss}{b}{n}\color{MyColor1}} 
{\thesection} {3pt} {} } 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		CAPTIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{caption}
\usepackage{subcaption}
%%%%%%%%%%%%%%%%%%%%%%%%
\captionsetup[figure]{labelfont={color=Turquoise}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		!!!EQUATION (ARRAY) --> USING ALIGN INSTEAD
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%using amsmath package to redefine eq. numeration (1.1, 1.2, ...) 
%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\theequation}{\thesection\arabic{equation}}

%set box background to grey in align environment 
\usepackage{etoolbox}% http://ctan.org/pkg/etoolbox
\makeatletter
\patchcmd{\@Aboxed}{\boxed{#1#2}}{\colorbox{black!15}{$#1#2$}}{}{}%
\patchcmd{\@boxed}{\boxed{#1#2}}{\colorbox{black!15}{$#1#2$}}{}{}%
\makeatother
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% DESIGN CIRCUITS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[siunitx, american, smartlabels, cute inductors, europeanvoltages]{circuitikz}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\makeatletter
\let\reftagform@=\tagform@
\def\tagform@#1{\maketag@@@{(\ignorespaces\textcolor{red}{#1}\unskip\@@italiccorr)}}
\renewcommand{\eqref}[1]{\textup{\reftagform@{\ref{#1}}}}
\makeatother
\usepackage{hyperref}
\hypersetup{colorlinks=true,citecolor=Black,urlcolor=MyColor1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREPARE TITLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\blue Educational Technology - Summer 2018 \\
\blueb Survey Questions}
\author{Alan Franzoni \& Hasti Ghabel} 

\date{\today}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\maketitle

\section {General Questions}

Please  answer below questions?\\
Age:\\
Sex:\\
Which category describes you best in the field of computer science?\\
-  Student\\
-  University professor, Staff, or school teacher\\
-  Employer\\


\section {Students}
\begin{enumerate}

	\item What is your major? Please specify:
	
	\item What is your highest degree level?
	\begin{itemize}
		\item No degree
		\item Bachelor's degree
		\item Post-Bachelors
		\item Master's degree
		\item Doctoral
		\item Professional certificate
	\end{itemize}
	
	\item What year are you in?
	\begin{itemize}
		\item Freshman
		\item Sophomore
		\item Junior
		\item Senior
		\item Other, Please specify:
	\end{itemize}
	
	\item Are you planning to continue your studies at higher level/ graduate levels?
	\begin{itemize}
		\item Yes
		\item No
		\item N/A
	\end{itemize}
	
	\item If you wanted to start your studies, would you choose another major? If YES, please specify a couple of reasons:
	
	\item What is your goal of studying in your major? Please select all that applies.
	\begin{itemize}
	\renewcommand{\labelitemi}{\scriptsize$\square$}
		\item I am very interested.
		\item Find a good job.
		\item Receiving high income in future.
		\item My friends and families encouraged me to study in this field.
		\item High demand in today's technology to accept computer scientists.
		\item Other, please specify:
	\end{itemize}
	
	\item What technical skills you expect to learn during your studies? Select all that applies
	\begin{itemize}
	\renewcommand{\labelitemi}{\scriptsize$\square$}
		\item Programming
		\item Algorithms
		\item Data structure
		\item Software architecture
		\item Artificial Intelligence and Machine Learning
		\item Other, please specify:
	\end{itemize}
	
	\item Among your above answers, what would you select as the most important skills you would like to learn?
	\begin{itemize}
		\item Programming
		\item Algorithms
		\item Data structure
		\item Software architecture
		\item Artificial Intelligence and Machine Learning
		\item Other, please specify:
	\end{itemize}
	
	\item What fields you prefer to work? scale from 1 to 7 (1 is the most preference, 7 is the least preference)
	\begin{table}[H]
 		\begin{tabular}{c r r r r r r r} 					% create eight columns
 		\hline\hline								% insert double line
 		Categories &  1  &  2   &  3  &  4  &  5  &  6  &  7 \\
	 	\hline
 		Science\\
 	 	Health\\
 		Business\\
 		Government\\
 		Education\\
		Law\\
		Security\\
 		\hline
 		\end{tabular}
 	\end{table}

	\item What do you expect to be your income range right after graduation?
	\begin{itemize}
		\item below \$30K
		\item \$30K - \$40K
		\item \$40K - \$50K
		\item \$50K - \$60K
		\item \$60K - \$70K
		\item \$70K - \$80K
		\item \$80K - \$90K
		\item \$90K - \$100K
		\item above \&100K
	\end{itemize}
	
	\item What would be the transition time from your graduation and finding a job? Please use 0 if you already have a job.
	
	\item How well you like your school?
	\begin{itemize}
		\item I am enthusiastic about it
		\item I like it
		\item I am more or less neutral about it
		\item I don't like it
	\end{itemize}
	
	\item Would you please shortly describe a couple of reasons that you like or dislike your school?
	
\end{enumerate}

Thank You!


\section{Universities/Schools (Professors, Staff, Teachers)}
\begin{enumerate}

	\item What is your role?
	\begin{itemize}
		\item Professor
		\item Teacher
		\item School/University Staff
		\item Other, please specify:
	\end{itemize}
	
	\item In your opinion, what is an important item for the university?
	\begin{itemize}
		\item University Ranking
		\item Number of graduates
		\item The number of ongoing research
		\item The amount of receiving the research fundings
		\item The number of students register in our program
	\end{itemize}
	
	\item What motivates you to continue being in your current role?
	\begin{itemize}
		\item Salary
		\item Research
		\item Improve technology-industry
		\item Other, Please specify.
	\end{itemize}
	
	\item why computer science or software engineering is an important major? 
	\begin{table}[H]
 		\begin{tabular}{c r r r r r} 					        % create six columns
 		\hline\hline								% insert double line
 		Item   &   Not at all  &   Unimportant   &   Neutral  &   Important   &   Very important \\
	 	\hline
 		It is useful\\ in all\\ other fields.\\
 	 	It is the most\\ demanding major.\\
 		Many students\\ register in this field.\\
 		There is a rapid\\ growth in \\technology-based \\jobs in industry.\\
 		\hline
 		\end{tabular}
 	\end{table}
	
	\item How students can be prepared to find a decent job after school? Please specify 2-3 items.
	
	\item What is the emphasis of your school? 
	
	\item In your opinion, what are the important topics for students to learn during their studies? Please rank from 1 to 5 (1 is the highest rank and 5 is the lowest).
	\begin{table}[H]
 		\begin{tabular}{c r r r r r} 					        % create six columns
 		\hline\hline								% insert double line
 		Item   &  1  &  2  &  3  &  4  &  5\\
	 	\hline
 		Programming:\\
 	 	Theories in computer science theories:\\
 		Research:\\
 		Prepare them for career\\ or job interview:\\
 		\hline
 		\end{tabular}
 	\end{table}

	\item What are the school emphasis? 1 means very strong Emphasis, and 5 means very weak emphasis.
	\begin{itemize}
		\item Developing academic, scholars, and intellectual qualities
		\item Critical, evaluative, and analytical thinking
		\item Human diversity
		\item Technical skills (e.g. programming)
		\item Occupation competences
		\item Accepting top students only
		\item Receive higher rankings
		\item Provide collaborative skills and good relationship with other students
		\item Career fairs and internships
	\end{itemize}
	
\end{enumerate}

\section{Industry}

\begin{enumerate}
	
	\item What is your position level:
	\begin{itemize}
		\item Developer
		\item Management
		\item Director/VP
		\item C-level
		\item Other, Please specify:
	\end{itemize}

	\item How long you have been in this organization?
	\begin{itemize}
		\item less than 1 year
		\item 1-3 years
		\item 4-6 years
		\item 7-9 years
		\item 10 years or more
	\end{itemize}

	\item Which category your company goes into:
	\begin{itemize}
		\item Banking
		\item Marketing
		\item Tele communication
		\item Law
		\item Health/Healthcare
		\item Government
		\item Security
		\item Start-ups
	\end{itemize}
	
	\item What the employers expect from fresh graduates? (rank from 1 to 8 question)
	\begin{itemize}
		\item Knowledge:
		\item Technical Skills:
		\item Attitude:
		\item Experience/Internships:
		\item University they graduated:
		\item grades:
		\item Curriculum:
		\item degree level:
	\end{itemize}

	\item Please rank your expectation from your employees's \textbf{knowledge} ? (rank from 1 to 8 question)
	\begin{itemize}
		\item Data structure:
		\item Algorithms:
		\item Database:
		\item Operating System
		\item Machine Learning and AI:
	\end{itemize}
	
	\item Please rank your expectation from your employees's \textbf{Skills} ? (rank from 1 to 8 question)
	\begin{itemize}
		\item Multiple Programming languages:
		\item Object-oriente design:
		\item Coding:
		\item Fast-learning
		\item Analytical thinking
		\item Presentation skills:
		\item Collaboration and team-work
		\item Communication
	\end{itemize}
	
	\item Please rank your expectation from your employees's \textbf{Attitude} ? (rank from 1 to 8 question)
	\begin{itemize}
		\item Self-motivated
		\item Self-Discipline
		\item Commitment
	\end{itemize}
	
	\item What are the benefits to hire a new graduate? Please specify 2-3 reasons.
	
	\item What are the disadvantages, if any, to hire a new graduate? Please specify 2-3 reasons.
	
	\item what is the average years of experience for hiring employees?
	


\end{enumerate}


\bibliography{bibliography.bib}{}
\bibliographystyle{IEEEtran}



\end{document}

